Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-01-03 apj.tex
polishing up

%
%
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=5.2in]{output18/dfitz.pdf}
%    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
%    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
%   \label{dfitz:fig}}
%\end{figure}
%
Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
as $R=const$), $R$ is held the same for all supernovae .  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
In the third (denoted as $R$-free), $A_V$ and $R$ are free for
each supernova, with a uniform prior $0\le A_V \le 1.8$, $1 \le R \le 8$.

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output18/AVs_mode_hist.pdf}
   \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
    \caption{Left: Histograms for the median $A_V$ determined for
each supernova, for the analyses assuming constant $R$, $\ln{R}$ from a Normal distribution, and $R$ from a uniform distribution.
To contrast, the corresponding $\gamma_0 k_0$ medians from our 2-parameter model is also shown.
Right: Posteriors for $R$ for the two analyses that constrain the $R$ distribution, and the histogram of
the median $R$ determine for each supernova in the $R$-free analysis.
   \label{AVRV:fig}}
\end{figure}

@@

>>>>

%
%
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=5.2in]{output18/dfitz.pdf}
%    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
%    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
%   \label{dfitz:fig}}
%\end{figure}
%
Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
as $R=const$), $R$ is held the same for all supernovae .  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
In the third (denoted as $R$-free), $A_V$ and $R$ are free for
each supernova, with a uniform prior $0\le A_V \le 1.8$, $1 \le R \le 8$.
(Note that for $R<2.2$, the model extrapolates beyond the range of the training set upon which it was trained.)

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output18/AVs_mode_hist.pdf}
   \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
    \caption{Left: Histograms for the median $A_V$ determined for
each supernova, for the analyses assuming constant $R$, $\ln{R}$ from a Normal distribution, and $R$ from a uniform distribution.
To contrast, the corresponding $\gamma_0 k_0$ medians from our 2-parameter model is also shown.  The means of the measurement
uncertainty over all supernovae are 0.13,   0.16,   0.11, and  0.05 mag respectively, roughly the size of the bin.
Right: Posteriors for $R$ for the two analyses that constrain the $R$ distribution, and the histogram of
the median $R$ determine for each supernova in the $R$-free analysis.
   \label{AVRV:fig}}
\end{figure}

@@

The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
non-zero.  Insofar that the $A_V$ and $R_V$
parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
is important.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
    \caption{Difference between per-supernova
$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
   \label{CCMF99:fig}}
\end{figure}
